Reproducible development environments with rix hello

### 2024-06-20 paper.qmd
Update paper.qmd

---
title: "Reproducible development environments with rix"
format:
    jss-pdf:
        keep-tex: true
    jss-html: default
author:
  - name: Bruno Rodrigues 
    affiliations:
      - name: Ministry of Research and Higher education, Luxembourg 
        department: Department of Statistics
        address: 18, Montée de la Pétrusse
        city: Luxembourg 
        country: Luxembourg 
        postal-code: 2327
      - Journal of Statistical Software
    orcid: 0000-0002-3211-3689
    email: bruno@brodrigues.co
    url: https://www.brodrigues.co 
  - name: Philipp Baumann
    affiliations:
      - Plus Affiliation
abstract: |
  In order create an analysis that is easily reproducible,
  it is not enough to write clean code and document it well. One
  must also make sure to clearly list all the dependencies of the analysis
  and ideally provide an easy way to install them.
  There are several tools that can be used to list dependencies and to
  make them easily installable by someone that wishes to reproduce a study,
  such as [Docker]{.proglang}, a containerization solution. This paper will
  present another tool that can be used to make projects reproducible,
  the Nix package manager, and an [R]{.proglang} package called [rix]{.pkg} that
  makes using Nix much simpler for users of [R]{.proglang}.

>>>>

---
title: "Reproducible development environments with rix hello"
format:
    jss-pdf:
        keep-tex: true
    jss-html: default
author:
  - name: Bruno Rodrigues 
    affiliations:
      - name: Ministry of Research and Higher education, Luxembourg 
        department: Department of Statistics
        address: 18, Montée de la Pétrusse
        city: Luxembourg 
        country: Luxembourg 
        postal-code: 2327
      - Journal of Statistical Software
    orcid: 0000-0002-3211-3689
    email: bruno@brodrigues.co
    url: https://www.brodrigues.co 
  - name: Philipp Baumann
    affiliations:
      - Plus Affiliation
abstract: |
  In order create an analysis that is easily reproducible,
  it is not enough to write clean code and document it well. One
  must also make sure to clearly list all the dependencies of the analysis
  and ideally provide an easy way to install them.
  There are several tools that can be used to list dependencies and to
  make them easily installable by someone that wishes to reproduce a study,
  such as [Docker]{.proglang}, a containerization solution. This paper will
  present another tool that can be used to make projects reproducible,
  the Nix package manager, and an [R]{.proglang} package called [rix]{.pkg} that
  makes using Nix much simpler for users of [R]{.proglang}.
